Clouds and Radiation in a mock-Walker Circulation

### 2020-08-26 Silvers_WalkerCell_response2reviewers.tex

\begin{enumerate}
  \item (Section 3)
    \begin{itemize}
      \item Is it possible to simply relate the difference in circulation/vertical velocity to the difference in CRE (e.g. using the
two box model for a given value of evaporation minus precipitation)?
      \item How does CRE compare to circulation strength throughout each simulation once the simulation has equilibrium
(this would give more data points than a single mean circulation/mean CRE comparison per simulation)?
    \end{itemize}
  \item (Section 4, Lines 407-409)
    \begin{itemize}
      \item Could the authors show correlations or scatter plots across simulations and across time within a given simulation
to back up their claim about the link between low-level cloud fraction, LWCRE, and convective versus large-scale
fraction of total precipitation?
      \item The causality claim also seems a bit bold given that LWCRE is the only effect that the authors turned on/off; it could
be for instance that surface latent heat fluxes plays as big of a role, which could be tested by turning the dependence
of latent heat fluxes on surface wind speed on/off, or by making the surface latent heat fluxes horizontally uniform
at each timestep. If the authors decide not to run additional experiments, I recommend nuancing that statement
given that Figure 7 shows that LWCRE is only responsible for part of this partitioning, and given that Figure 6 is
so hard to read (which could be easily improve by making the P25 and P25L different colors, etc.).
    \end{itemize}
  \item (Section 5)
    \begin{itemize}
      \item The logical flow of the CRM/GCM comparison is relatively easy to follow, but I was wondering if the authors
could expand on their baseline result that the CRM configuration leads to more upper-level clouds while the GCM
configuration leads to more lower-level clouds. Would it be possible to compare the vertically-resolved water species
budget across simulations to understand this difference?
      \item It is reassuring that this result is consistent with [5]; would it be possible to similarly trace back this difference to a
discrepancy in shallow cloud mixing, e.g. by comparing the vertical transport of water vapor between the boundary
layer and the lower troposphere across experiments?
    \end{itemize}
\end{enumerate}

\subsubsection{Assessing the realism of the simulated mock-Walker cell}

As the authors point out (L67), the Walker cell setup can be compared to observations from the Pacific region. As their
results show large differences between the E25/P25 and the E2/E1 simulations (e.g. L420-421), how can the reader
assess which simulation best captures the Walker cell’s hydrological cycle?
Although a direct comparison is impossible because of the idealized mock-Walker cell setup, I would highly suggest
adding observational and/or meteorological reanalysis data to at least some of Section 5’s figures (Figure 8-13) to comment
on which configuration leads to the most observationally consistent Walker cell. To facilitate the comparison, the authors
could e.g. choose a period of time where the Pacific’s zonal surface temperature gradient is in the range of the experiments
listed in Table 1 $(\Delta SST/ \Delta x = 10^{-4} - 10^{-3} K/km).  $

\subsection{Minor comments}

You will find 15 minor comments attached to the annotated PDF of the manuscript. Additional comments that apply
throughout the paper are listed below:
\begin{itemize}
  \item Labeling all figure panels using the conventional notation a/b/c/d (e.g. Figure 1, 2, etc.)
  \item Make titles more formal (e.g. Figure 13) and using a consistently large font size across figures (for instance, the
titles are easy to read in Figures 9 and 10, but not in Figures 11, 12, and 13)

  \textcolor{blue}{The font size for axis and titles in Figure 12 has been increased, x-axis label for Figure 12d corrected to read only units.}
\end{itemize}

%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS
%

%\acknowledgments
%Enter acknowledgments, including your data availability statement, here.

%% ------------------------------------------------------------------------ %%
%% References and Citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \bibliography{<name of your .bib file>} don't specify the file extension
%
% don't specify bibliographystyle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{ enter your bibtex bibliography filename here }

%Reference citation instructions and examples:
%
% Please use ONLY \cite and \citeA for reference citations.
% \cite for parenthetical references
% ...as shown in recent studies (Simpson et al., 2019)
% \citeA for in-text citations
% ...Simpson et al. (2019) have shown...
%
%
%...as shown by \citeA{jskilby}.
%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
%...has been shown \cite{jskilbye}.
%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
%... \cite <i.e.>[]{lewin76,carson86,bartoldy02,rinaldi03}.
%...has been shown by \cite <e.g.,>[and others]{lewin76}.
%
% apacite uses < > for prenotes and [ ] for postnotes
% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
%

\end{document}

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

% If you are using line numbers, remember to surround
% equations with \begin{linenomath*}...\end{linenomath*}

%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}
